Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-03-17 demystify.tex
updates

          \item \emph{Grades might be important}, depends on the reputation of \emph{your school} (\autoref{sec:your-school}). While good grades might not help much, bad ones will likley hurt your case.
          \item \emph{Standard tests are not important} (\autoref{sec:standard-tests}). GRE \emph{is not} even required. Spend your time on something else! For standard English test, just do enough to pass the minimum requirements.

@@

For external fellowships including those from the US government and tech companies (e.g., Google, Microsoft, Facebook), you will need to apply.  Fellowships from US government would likely require US citizenship or residency. % However, tech companies including Google, Microsoft, Facebook have fellowships that international students can apply for.
Prestigious external fellowships typically require a clear and good research plan, so it might be a good idea to wait until at least your second year to have research experience and even publication before applying. Remember, you're competing with the top PhD students at top universities worldwide.

@@

In general, fellowship, especially competitive ones from the government or company, is prestigious, and you will stand out if you get one.  Every PhD student has pubs, but only few  would have NSF Graduate or Microsoft fellowship. In fact, these are so prestigious that even if you didn't get it but make it to the final round or even ``honorable mentioning'', school will still mention you on their website and you still should put it on your CV.

>>>>

          \item \emph{Grades might be important}, depends on the reputation of \emph{your school} (\autoref{sec:your-school}). While good grades might not help much, bad ones will likley hurt your case.
          \item \emph{Standard tests are not important} (\autoref{sec:standard-tests}). GRE \emph{is not} even required. Spend your time on something else! For standard English tests (not required for domestic students), just do enough to pass the minimum requirements.

@@

For external fellowships including those from the US government and tech companies (e.g., Google, Microsoft, Facebook), you will need to apply.  % However, tech companies including Google, Microsoft, Facebook have fellowships that international students can apply for.
Prestigious external fellowships typically require a clear and good research plan, so it might be a good idea to wait until at least your second year to have research experience and even publication before applying. Remember, you're competing with the top PhD students at top universities worldwide.

@@

In addition to general fellowships that are available to all students, there are also specic fellowships, e.g., for US citizen and permanent residents, for underrepresented minority (URM) students (\autoref{sec:urm}), and for students from specific countries. In short, there are many fellowships available, so you should look for them and apply.

In general, fellowships, especially those that are open to everyone, are highly competitive and prestigious, and you will stand out if you get one.  Every PhD student has pubs, but only few  would have NSF Graduate or Microsoft fellowship. In fact, these are so prestigious that even if you didn't get it but make it to the final round or even ``honorable mentioning'', school will still mention you on their website and you still should put it on your CV.
